\newpage
\thispagestyle{empty}
\begin{center}
    \vspace*{1cm}
    \textbf{\LARGE CERTIFICATE} \\[1.5cm]
\end{center}

\noindent This is to certify that the project report entitled \textbf{"PROJECT TITLE"} submitted by \textbf{YOUR NAME} (Reg. No. YOUR REG NO) in partial fulfillment of the requirements for the award of the degree of \textbf{DEGREE NAME} in \textbf{DEPARTMENT NAME} is a bona fide record of the work carried out under my supervision.

\vspace{2.5cm}

\noindent
\begin{minipage}[t]{0.45\textwidth}
    \textbf{INTERNAL GUIDE NAME} \\
    Designation \\
    Department
\end{minipage}
\hfill
\begin{minipage}[t]{0.45\textwidth}
    \begin{flushright}
        \textbf{HOD NAME} \\
        Head of Department \\
        Department
    \end{flushright}
\end{minipage}

\vspace{2cm}
\begin{center}
    External Examiner
\end{center}

\newpage
\thispagestyle{empty}
\begin{center}
    \vspace*{1cm}
    \textbf{\LARGE SUPERVISOR’S CERTIFICATE} \\[1.5cm]
\end{center}

\noindent This is to certify that \textbf{YOUR NAME} has successfully completed the internship at \textbf{COMPANY NAME} from START DATE to END DATE. During this period, he/she worked on the project titled \textbf{"PROJECT TITLE"}.

\noindent He/She has demonstrated good technical skills and conduct during the internship. We wish him/her all the best for future endeavors.

\vspace{3cm}

\begin{flushright}
    \textbf{SUPERVISOR NAME} \\
    Designation \\
    Company Name
\end{flushright}

\newpage
\thispagestyle{empty}
\begin{center}
    \vspace*{1cm}
    \textbf{\LARGE ACKNOWLEDGEMENT} \\[1.5cm]
\end{center}

\noindent I would like to express my sincere gratitude to my internship supervisor, \textbf{SUPERVISOR NAME}, at \textbf{COMPANY NAME}, for their valuable guidance, encouragement, and support throughout the course of this internship.

\noindent I am also deeply grateful to my internal guide, \textbf{INTERNAL GUIDE NAME}, and the Head of the Department, \textbf{HOD NAME}, for their continuous motivation and advice.

\noindent Finally, I would like to thank my family and friends for their unwavering support and understanding during the completion of this project.

\vspace{3cm}

\begin{flushright}
    \textbf{YOUR NAME}
\end{flushright}

\newpage
\thispagestyle{empty}
\begin{center}
    \vspace*{1cm}
    \textbf{\LARGE ABSTRACT} \\[1.5cm]
\end{center}

\noindent [Write your abstract here. It should be a concise summary of the entire report, covering the problem statement, the methodology or technologies used, the work performed during the internship, and the key results or conclusions.]
